PANCHANGE_data_preprocessing

### 2020-08-26 PANCHANGE_data_preprocessing2020-07-15.Rmd
added none_of_the_above columns to all mhd

edgi.mhd.raw.id <- edgi.mhd.raw %>%
  drop_na(externalDataReference) %>% # Drop NAs
  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
  mutate(ID = as.numeric(ID)) %>%
  select(
    Sample, # Sample
    ID, # ID
    mhd.anorexia_nervosa,
    mhd.atypical_anorexia_nervosa,
    mhd.bulimia_nervosa,
    mhd.atypical_bulimia_nervosa,
    mhd.bingeeating_disorder,
    mhd.atypical_bingeeating_disorder
  ) %>%
  add_numeric(., exclude = exclude_cols) %>%
  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
  mutate_if(is.numeric, ~na_if(., -99)) %>%
  mutate_if(is.numeric, ~na_if(., -77)) %>%
  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

@@

  edgi.mhd2.raw.id <- edgi.mhd2.raw %>%
    drop_na(externalDataReference) %>% # Drop NAs
    distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
    separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
    mutate(ID = as.numeric(ID)) %>%
    select(
      Sample, # Sample
      ID, # ID
    mhd.depression = demographics.depression,
    mhd.pregnancy_depression = demographics.pregnancy_depression,
    mhd.premenstrual_dysphoric_disorder_pmdd = demographics.premenstrual_dysphoric_disorder_pmdd,
    mhd.anxiety_nerves_or_generalised_anxiety_disorder = demographics.anxiety_nerves_or_generalised_anxiety_disorder,
    mhd.social_anxiety_or_social_phobia = demographics.social_anxiety_or_social_phobia,
    mhd.specific_phobia_e.g._phobia_of_flying = demographics.specific_phobia_e.g._fear_of_flying, # fear instead of phobia
    mhd.agoraphobia = demographics.agoraphobia,
    mhd.panic_disorder = demographics.panic_disorder,
    mhd.panic_attacks = demographics.panic_attacks,
    mhd.obsessivecompulsive_disorder_ocd = demographics.obsessivecompulsive_disorder_ocd,
    mhd.obsessive_compulsive_related_disorders = demographics.obsessive_compulsive_related_disorders,
    mhd.body_dysmorphic_disorder_bdd = demographics.body_dysmorphic_disorder,
    mhd.mania_hypomania_bipolar_or_manicdepression = demographics.mania_hypomania_bipolar_or_manicdepression,
    mhd.schizophrenia = demographics.schizophrenia,
    mhd.type_psychosis_psychotic_illness = demographics.psychosis_type_psychotic_illness, # word type psychosis changed order compared to GLAD 
    mhd.personality_disorder_diagnosed = demographics.diagnosed_personality_disorder, # named differently in EDGI
    mhd.posttraumatic_stress_disorder_ptsd = demographics.posttraumatic_stress_disorder_ptsd,
    mhd.autism_aspergers_or_autistic_spectrum_disorder = demographics.autism_spectrum_disorder_asd, # different name in EDGI
    mhd.body_dysmorphic_disorder_bdd = demographics.body_dysmorphic_disorder,
    mhd.personality_disorder = demographics.personality_disorder, # routing variable in EDGI is named differently; renamed here to match GLAD
    mhd.attention_deficit_hyperactivity_disorder = demographics.attention_deficit_hyperactivity_disorder
    ) %>%
    add_column(
      mhd.schizoaffective_disorder = NA_character_
    ) %>%
    add_numeric(., exclude = exclude_cols_mhd2) %>%
    mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
    mutate_if(is.numeric, ~na_if(., -99)) %>%
    mutate_if(is.numeric, ~na_if(., -77)) %>%
    mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
    mutate_if(is.factor, ~na_if(., "Don't know")) %>%
    mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
    mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
    mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
    mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
    mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
    mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

@@

nbr.mhd.raw.id <- nbr.mhd.raw %>%
  drop_na(subjectid) %>% # Drop NAs
  distinct(subjectid, .keep_all = TRUE) %>% # Remove duplicates based on ID
  separate(subjectid, into = c("Sample", "ID.intm"), sep = 6) %>% # Split ID in Sample and Number
  separate(ID.intm, into = "ID", sep = 7) %>%
  mutate(
    ID = as.numeric(ID)) %>%
  select(
    Sample, # Sample
    ID, # ID
    starts_with("mhd."),
    mhd.specific_phobia_e.g._phobia_of_flying = mhd.specific_phobia_e.g._fear_of_flying,
    mhd.type_psychosis_psychotic_illness = mhd.psychosis_type_psychotic_illness,
    mhd.autism_aspergers_or_autistic_spectrum_disorder = mhd.autism_spectrum_disorder_asd,
    mhd.anorexia_nervosa_unc = mhd.anorexia_nervosa,
    mhd.atypical_anorexia_nervosa_unc = mhd.atypical_anorexia_nervosa,
    mhd.bulimia_nervosa_unc = mhd.bulimia_nervosa,
    mhd.bingeeating_disorder_unc = mhd.bingeeating_disorder
  ) %>%
  add_column(
    mhd.schizoaffective_disorder = NA #NBR doesn't ask about schizoaffective disorder. This means the column das not exist in the data set
  ) %>% 
  add_numeric(., exclude = exclude_cols) %>%
  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
  mutate_if(is.numeric, ~na_if(., -99)) %>%
  mutate_if(is.numeric, ~na_if(., -77)) %>%
  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

@@

ramp.mhd.raw.id <- ramp.mhd.raw %>%
  drop_na(`Login ID`) %>% # Drop NAs
  distinct(`Login ID`, .keep_all = TRUE) %>% # Remove duplicates based on ID
  separate(`Login ID`, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
  separate(ID, into = "ID", sep = 7) %>%
  mutate(
    ID = as.numeric(ID)) %>%
  select(
    Sample, # Sample
    ID, # ID
    mhd.depression = NA.30.depression,
    mhd.pregnancy_depression = NA.30.pregnancy_depression,
    mhd.premenstrual_dysphoric_disorder_pmdd = NA.30.premenstrual_dysphoric_disorder_pmdd,
    mhd.mania_hypomania_bipolar_or_manicdepression = NA.30.mania_hypomania_bipolar_or_manicdepression,
    mhd.anxiety_nerves_or_generalised_anxiety_disorder = NA.30.anxiety_nerves_or_generalised_anxiety_disorder,
    mhd.social_anxiety_or_social_phobia = NA.30.social_anxiety_or_social_phobia,
    mhd.specific_phobia_e.g._phobia_of_flying = NA.30.specific_phobia_e.g._phobia_of_flying,
    mhd.agoraphobia = NA.30.agoraphobia,
    mhd.panic_disorder = NA.30.panic_disorder,
    mhd.panic_attacks = NA.30.panic_attacks,
    mhd.posttraumatic_stress_disorder_ptsd = NA.30.posttraumatic_stress_disorder_ptsd,
    mhd.obsessivecompulsive_disorder_ocd = NA.30.obsessivecompulsive_disorder_ocd, 
    mhd.body_dysmorphic_disorder_bdd = NA.30.body_dysmorphic_disorder_bdd,
    mhd.skin_picking_obsessive_compulsive = NA.30.skin_picking_obsessive_compulsive,
    mhd.anorexia_nervosa = NA.30.anorexia_nervosa,
    mhd.atypical_anorexia_nervosa = NA.30.atypical_anorexia_nervosa,
    mhd.bulimia_nervosa = NA.30.bulimia_nervosa,
    mhd.bingeeating_disorder = NA.30.psychological_overeating_or_bingeeating_disorder,
    mhd.schizophrenia = NA.30.schizophrenia,
    mhd.schizoaffective_disorder = NA.30.schizoaffective_disorder,
    mhd.type_psychosis_psychotic_illness = NA.30.psychosis_type_psychotic_illness,
    mhd.personality_disorder = NA.30.personality_disorder,
    mhd.autism_aspergers_or_autistic_spectrum_disorder = NA.30.autism_aspergers_or_autistic_spectrum_disorder,
    mhd.attention_deficit_hyperactivity_disorder = NA.30.attention_deficit_hyperactivity_disorder,
    mhd.personality_disorder_diagnosed = NA.30.personality_disorder_diagnosed
  ) %>%
  add_numeric(., exclude = exclude_cols) %>%
  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
  mutate_if(is.numeric, ~na_if(., -99)) %>%
  mutate_if(is.numeric, ~na_if(., -77)) %>%
  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

@@

>>>>

edgi.mhd.raw.id <- edgi.mhd.raw %>%
  drop_na(externalDataReference) %>% # Drop NAs
  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
  mutate(ID = as.numeric(ID)) %>%
  select(
    Sample, # Sample
    ID, # ID
    mhd.anorexia_nervosa,
    mhd.atypical_anorexia_nervosa,
    mhd.bulimia_nervosa,
    mhd.atypical_bulimia_nervosa,
    mhd.bingeeating_disorder,
    mhd.atypical_bingeeating_disorder,
    mhd.ed_none_of_the_above = mhd.none_of_the_above
  ) %>%
  add_numeric(., exclude = exclude_cols) %>%
  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
  mutate_if(is.numeric, ~na_if(., -99)) %>%
  mutate_if(is.numeric, ~na_if(., -77)) %>%
  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

@@

  edgi.mhd2.raw.id <- edgi.mhd2.raw %>%
    drop_na(externalDataReference) %>% # Drop NAs
    distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
    separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
    mutate(ID = as.numeric(ID)) %>%
    select(
      Sample, # Sample
      ID, # ID
    mhd.depression = demographics.depression,
    mhd.pregnancy_depression = demographics.pregnancy_depression,
    mhd.premenstrual_dysphoric_disorder_pmdd = demographics.premenstrual_dysphoric_disorder_pmdd,
    mhd.anxiety_nerves_or_generalised_anxiety_disorder = demographics.anxiety_nerves_or_generalised_anxiety_disorder,
    mhd.social_anxiety_or_social_phobia = demographics.social_anxiety_or_social_phobia,
    mhd.specific_phobia_e.g._phobia_of_flying = demographics.specific_phobia_e.g._fear_of_flying, # fear instead of phobia
    mhd.agoraphobia = demographics.agoraphobia,
    mhd.panic_disorder = demographics.panic_disorder,
    mhd.panic_attacks = demographics.panic_attacks,
    mhd.obsessivecompulsive_disorder_ocd = demographics.obsessivecompulsive_disorder_ocd,
    mhd.obsessive_compulsive_related_disorders = demographics.obsessive_compulsive_related_disorders,
    mhd.body_dysmorphic_disorder_bdd = demographics.body_dysmorphic_disorder,
    mhd.mania_hypomania_bipolar_or_manicdepression = demographics.mania_hypomania_bipolar_or_manicdepression,
    mhd.schizophrenia = demographics.schizophrenia,
    mhd.type_psychosis_psychotic_illness = demographics.psychosis_type_psychotic_illness, # word type psychosis changed order compared to GLAD 
    mhd.personality_disorder_diagnosed = demographics.diagnosed_personality_disorder, # named differently in EDGI
    mhd.posttraumatic_stress_disorder_ptsd = demographics.posttraumatic_stress_disorder_ptsd,
    mhd.autism_aspergers_or_autistic_spectrum_disorder = demographics.autism_spectrum_disorder_asd, # different name in EDGI
    mhd.body_dysmorphic_disorder_bdd = demographics.body_dysmorphic_disorder,
    mhd.personality_disorder = demographics.personality_disorder, # routing variable in EDGI is named differently; renamed here to match GLAD
    mhd.attention_deficit_hyperactivity_disorder = demographics.attention_deficit_hyperactivity_disorder,
    mhd.none_of_the_above = demographics.none_of_the_above.1,
    mhd.none_of_the_above.1 = demographics.none_of_the_above.8
    ) %>%
    add_column(
      mhd.schizoaffective_disorder = NA_character_
    ) %>%
    add_numeric(., exclude = exclude_cols_mhd2) %>%
    mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
    mutate_if(is.numeric, ~na_if(., -99)) %>%
    mutate_if(is.numeric, ~na_if(., -77)) %>%
    mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
    mutate_if(is.factor, ~na_if(., "Don't know")) %>%
    mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
    mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
    mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
    mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
    mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
    mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

@@

nbr.mhd.raw.id <- nbr.mhd.raw %>%
  drop_na(subjectid) %>% # Drop NAs
  distinct(subjectid, .keep_all = TRUE) %>% # Remove duplicates based on ID
  separate(subjectid, into = c("Sample", "ID.intm"), sep = 6) %>% # Split ID in Sample and Number
  separate(ID.intm, into = "ID", sep = 7) %>%
  mutate(
    ID = as.numeric(ID)) %>%
  select(
    Sample, # Sample
    ID, # ID
    starts_with("mhd."),
    mhd.specific_phobia_e.g._phobia_of_flying = mhd.specific_phobia_e.g._fear_of_flying,
    mhd.type_psychosis_psychotic_illness = mhd.psychosis_type_psychotic_illness,
    mhd.autism_aspergers_or_autistic_spectrum_disorder = mhd.autism_spectrum_disorder_asd,
    mhd.anorexia_nervosa_unc = mhd.anorexia_nervosa,
    mhd.atypical_anorexia_nervosa_unc = mhd.atypical_anorexia_nervosa,
    mhd.bulimia_nervosa_unc = mhd.bulimia_nervosa,
    mhd.bingeeating_disorder_unc = mhd.bingeeating_disorder,
    mhd.ed_none_of_the_above = mhd.none_of_the_above.2
  ) %>%
  add_column(
    mhd.schizoaffective_disorder = NA #NBR doesn't ask about schizoaffective disorder. This means the column das not exist in the data set
  ) %>% 
  add_numeric(., exclude = exclude_cols) %>%
  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
  mutate_if(is.numeric, ~na_if(., -99)) %>%
  mutate_if(is.numeric, ~na_if(., -77)) %>%
  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

@@

ramp.mhd.raw.id <- ramp.mhd.raw %>%
  drop_na(`Login ID`) %>% # Drop NAs
  distinct(`Login ID`, .keep_all = TRUE) %>% # Remove duplicates based on ID
  separate(`Login ID`, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
  separate(ID, into = "ID", sep = 7) %>%
  mutate(
    ID = as.numeric(ID)) %>%
  select(
    Sample, # Sample
    ID, # ID
    mhd.depression = NA.30.depression,
    mhd.pregnancy_depression = NA.30.pregnancy_depression,
    mhd.premenstrual_dysphoric_disorder_pmdd = NA.30.premenstrual_dysphoric_disorder_pmdd,
    mhd.mania_hypomania_bipolar_or_manicdepression = NA.30.mania_hypomania_bipolar_or_manicdepression,
    mhd.anxiety_nerves_or_generalised_anxiety_disorder = NA.30.anxiety_nerves_or_generalised_anxiety_disorder,
    mhd.social_anxiety_or_social_phobia = NA.30.social_anxiety_or_social_phobia,
    mhd.specific_phobia_e.g._phobia_of_flying = NA.30.specific_phobia_e.g._phobia_of_flying,
    mhd.agoraphobia = NA.30.agoraphobia,
    mhd.panic_disorder = NA.30.panic_disorder,
    mhd.panic_attacks = NA.30.panic_attacks,
    mhd.posttraumatic_stress_disorder_ptsd = NA.30.posttraumatic_stress_disorder_ptsd,
    mhd.obsessivecompulsive_disorder_ocd = NA.30.obsessivecompulsive_disorder_ocd, 
    mhd.body_dysmorphic_disorder_bdd = NA.30.body_dysmorphic_disorder_bdd,
    mhd.skin_picking_obsessive_compulsive = NA.30.skin_picking_obsessive_compulsive,
    mhd.anorexia_nervosa = NA.30.anorexia_nervosa,
    mhd.atypical_anorexia_nervosa = NA.30.atypical_anorexia_nervosa,
    mhd.bulimia_nervosa = NA.30.bulimia_nervosa,
    mhd.bingeeating_disorder = NA.30.psychological_overeating_or_bingeeating_disorder,
    mhd.schizophrenia = NA.30.schizophrenia,
    mhd.schizoaffective_disorder = NA.30.schizoaffective_disorder,
    mhd.type_psychosis_psychotic_illness = NA.30.psychosis_type_psychotic_illness,
    mhd.personality_disorder = NA.30.personality_disorder,
    mhd.autism_aspergers_or_autistic_spectrum_disorder = NA.30.autism_aspergers_or_autistic_spectrum_disorder,
    mhd.attention_deficit_hyperactivity_disorder = NA.30.attention_deficit_hyperactivity_disorder,
    mhd.personality_disorder_diagnosed = NA.30.personality_disorder_diagnosed,
    mhd.none_of_the_above = NA.30.none_of_these,
    mhd.none_of_the_above.1 = NA.30.none_of_these.1
  ) %>%
  add_numeric(., exclude = exclude_cols) %>%
  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
  mutate_if(is.numeric, ~na_if(., -99)) %>%
  mutate_if(is.numeric, ~na_if(., -77)) %>%
  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

@@

```{r}
mhd.raw.id %>%
  select(
    control,
    mhd.none_of_the_above,
    mhd.none_of_the_above.1
  )

mhd.raw.id %>%
  group_by(mhd.none_of_the_above.1) %>%
  count(
    control,
    mhd.none_of_the_above
  )

mhd.raw.id %>%
  count(
    control,
    age_
  )
```

```{r Check personality_cluster_c}
if(GLAD == TRUE | NBR == TRUE | RAMP == TRUE) {
mhd.raw.id %>%
  select(
    control,
    depressive_disorders_numeric,
    anxiety_disorders_numeric,
    eating_disorders_numeric,
    obsessive_compulsive_disorders_numeric,
    psychotic_disorders_numeric,
    mhd.mania_hypomania_bipolar_or_manicdepression_numeric,
    mhd.posttraumatic_stress_disorder_ptsd_numeric,
    autism_spectrum_disorder_numeric,
    mhd.attention_deficit_hyperactivity_disorder_numeric,
    mhd.personality_disorder_numeric, 
  )
}
```
